---
title: 'hw04: Sketching graphs'
author: | 
  | Kenji Sato
  | Kobe University
  | mail@kenjisato.jp
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    includes:
      in_header: asset/latex/custom.sty
    keep_tex: no
    latex_engine: pdflatex
    number_sections: yes
    template: null
    toc: no
  bookdown::html_document2: default
documentclass: scrartcl
---

# Overview

Think of a situation where you write your thesis, a paper, slides, or weekly 
reports to your advisor or future you. You may have an idea for the proof 
of your conjecture. You may want to discuss why the mechanism you describe 
in the article/note/journal works as you expect. 

You can demonstrate your idea most unambiguously with mathematical expressions. 
To reveal the economic intuition behind your theory, you must 
elaborate on the mechanism in words. Often times, drawing a graphical sketch 
of your theory is the most effective way to convey your idea to the reader.

Since sketching graphs is an important skill for academic communication, 
I would recommend all of you to build your own routine to draw nice graphs 
on a computer. 

## Purpose {-}

To learn 

* how to draw a sketch of a graph on computers and 
* how to embed it in an R Markdown document.

Here, in this `problem.pdf`, I show you my routine. Imitate and extend it 
if you don't have yours already or if you think yours is not as good as mine. 

If you think you have a better way, you don't need to learn from me. Just 
follow your routine to create a picture file and embed it in the document 
with the function I show you later in this document. 

## Instructions {-}

In this assignment, you will

- clone the assignment repository and make a working branch (eg. `solution` branch);
- draw graphs and put the file in `figure` folder (see Section \@ref(problem)); 
- write the solutions in `solution.Rmd`; 
- commit `solution.Rmd` and `solution.pdf` together with the picture file(s); and 
- open a Pull Request.
 
# My routine

## Draw {-}

I use Keynote, a presentation application for Mac, to draw graphs. 
If you work on Windows, PowerPoint is an alternative. As a sample I 
attach the presentation file I used for a class. Uncompress 
`asset/images/solow_model.key.zip` and open `solow_model.key` with 
Keynote for Mac to see how I draw the graphs and set fonts for mathematical 
expressions.^[My favorite choice is Palatino fonts in bold italics, which 
go well with `mathpazo` package of LaTeX. To embed more complex mathematical 
expressions in a presentation file, I use LaTeXit, which converts a LaTeX 
code snippet into an image of the rendered math expressions.] 


## Export {-}

Export the presentation file to a single PDF or multiple image files 
(JPEG or PNG). Put them somewhere close to the R Markdown file.
I usually put the original file and the exported together under a folder
named `figures` or `images`.

The resulting PDF file is stored in `asset/images/solow_model.pdf` as 
a sample.

## Embed {-}

Now that we have the graphs, let's move to RStudio and to an R Markdown file.

Set global knit options at the beginning of the document with a code chunk similar to below. This set the default figure width to 14cm and default alignment to center. 

Your `solution.Rmd` already has this chunk.

    `r ''````{r, include=FALSE}
    knitr::opts_chunk$set(fig.align = 'center', out.width = "12cm")
    ```

```{r, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center', out.width = "12cm")
```

To embed the first page of the PDF, You can use a code chunk as follows: 
    
    `r ''````{r solow1, fig.cap="(ref:solow1)", out.extra="page=1", echo=FALSE}
    knitr::include_graphics("asset/images/solow_model.pdf")
    ```

This R code chunk produces Figure \@ref(fig:solow1). I used cross-reference command `\@ref(fig:solow1)` here. Note that the chunk label (`solow1`) with prefix `fig:` is used as a pointer to the figure. 

Please have a look at the source file (`problem.Rmd`) to see how I take advantage of 
text reference for the caption (`fig.cap` option).^[For more detail, see  https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#text-references]
This feature comes in handy when the caption is long.

The chunk option, `out.extra="page=1"`, is a special option used when including a page 
from a multiple-page PDF file. `out.extra="page=n"` includes n-th page of the PDF 
file specified as the argument to `knitr::include_graphics()` function.

```{r solow1, fig.cap="(ref:solow1)", out.extra="page=1",echo=FALSE}
knitr::include_graphics("asset/images/solow_model.pdf")
```

(ref:solow1) Solow Model


```{r solow2, fig.cap="(ref:solow2)", out.extra="page=7",echo=FALSE}
knitr::include_graphics("asset/images/solow_model.pdf")
```

(ref:solow2) Increase in $s$


# Problem

Produce a figure similar to Figure \@ref(fig:solow2) but for the cases of

1. a sudden decrease of $s$; and 
1. a sudden increase of $n$.

Put the file in `figures`. In the body of the document, explain what happens to $k$ after the parameter change. 

The document must have all of the following.

* Correct graphs
* Reasonable captions attached to them and 
* At least one reference to each Figure


